Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
78 done. need to flag the ones that are unclear between large shrub and small tree. ask the group for ideas

  if(genusSpecies == "Pseudotsuga menziesii"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Douglas-fir"}

@@

@@

@@

taxon_pft_lookup$pft(taxon_pft_lookup$genusSpecies == "Pseudotsuga menziesii") <- "coniferous_forest"
```

>>>>

  if(genusSpecies == "Abies amabilis"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Pacific silver fir"}

  else if(genusSpecies == "Abies balsamea"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "balsam fir"}

  else if(genusSpecies == "Abies lasiocarpa"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "subalpine fir"}

  else if(genusSpecies == "Acacia greggii"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "catclaw acacia"}

  else if(genusSpecies == "Acer barbatum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Southern sugar maple"}

  else if(genusSpecies == "Acer negundo"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "boxelder"}

  else if(genusSpecies == "Acer saccharinum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "silver maple"}

@@

  else if(genusSpecies == "Aloysia wrightii"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "Wright's beebrush"}

  else if(genusSpecies == "Amelanchier laevis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Allegheny serviceberry"}

  else if(genusSpecies == "Amyris elemifera"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "sea torchwood"}

  else if(genusSpecies == "Artemisia tridentata"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "big sagebrush"}

  else if(genusSpecies == "Atriplex canescens"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "fourwing saltbush"}

  else if(genusSpecies == "Atriplex confertifolia"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "shadscale saltbush"}

  else if(genusSpecies == "Betula lenta"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sweet birch"}

  else if(genusSpecies == "Betula neoalaskana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "resin birch"}

  else if(genusSpecies == "Betula nigra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "river birch"}

  else if(genusSpecies == "Betula sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "birch"}

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "strongbark"}

  else if(genusSpecies == "Bursera simaruba"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"  # "semi-deciduous"
    taxon_pft_lookup$commonName[i] = "gumbo limbo"}

  else if(genusSpecies == "Carpinus caroliniana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "American hornbeam"}

  else if(genusSpecies == "Carya aquatica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "water hickory"}

  else if(genusSpecies == "Carya cordiformis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "bitternut hickory"}

  else if(genusSpecies == "Carya illinoinensis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "pecan"}

  else if(genusSpecies == "Carya ovalis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "red hickory"}

  else if(genusSpecies == "Carya ovata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "shagbark hickory"}

  else if(genusSpecies == "Carya tomentosa"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "mockernut hickory"}

  else if(genusSpecies == "Celtis laevigata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sugarberry"}

  else if(genusSpecies == "Cercis canadensis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "eastern redbud"}

  else if(genusSpecies == "Chrysothamnus viscidiflorus"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "yellow rabbitbrush"}

  else if(genusSpecies == "Cordia collococca"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "red manjack"}

  else if(genusSpecies == "Cornus drummondii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "roughleaf dogwood"}

  else if(genusSpecies == "Cornus florida"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "flowering dogwood"}

  else if(genusSpecies == "Diospyros virginiana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "common persimmon"}

  else if(genusSpecies == "Ephedra trifurca"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "longleaf jointfir"}

  else if(genusSpecies == "Ericameria laricifolia"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "turpentine bush"}

  else if(genusSpecies == "Exostema caribaeum"){
    taxon_pft_lookup$pft[i] = "woody_shrub"  # "evergreen shrub or small tree" 
    taxon_pft_lookup$commonName[i] = "Caribbean princewood"}

  else if(genusSpecies == "Fraxinus nigra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black ash"}

  else if(genusSpecies == "Fraxinus pennsylvanica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "green ash"}

  else if(genusSpecies == "Fraxinus sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "ash"}

  else if(genusSpecies == "Gleditsia triacanthos"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "honey locust"}

  else if(genusSpecies == "Gutierrezia sarothrae"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "broom snakeweed"}

  else if(genusSpecies == "Halesia sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"  # small, deciduous, understory tree 
    taxon_pft_lookup$commonName[i] = "silverbell"}

  else if(genusSpecies == "Hamamelis virginiana"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "American witchhazel"}

  else if(genusSpecies == "Ilex montana"){
    taxon_pft_lookup$pft[i] = "NA"
    taxon_pft_lookup$commonName[i] = "mountain holly"}

  else if(genusSpecies == "Pseudotsuga menziesii"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Douglas-fir"}

@@

  else if(genusSpecies == "Picea glauca"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "white spruce"}

  else if(genusSpecies == "Ulmus crassifolia"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "cedar elm"}

  else if(genusSpecies == "Quercus stellata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "post oak"}

@@

```
